The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-09-20 dit-paper_ieee.tex
rewording

		The DBF test gives us a list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility. They
		can all be written in the following way:
		\begin{equation}
			\sum_{i=1}^{n}  n_i(t_1, t_2) \cdot C_i \leq t_2 - t_1 \; \forall t_1,t_2 \mid 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

  To summarize, we reduced the description of the C-space from an infinite number
  of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
  values of $t_2$ correspond to job deadlines. Note that the number of
  constraints is still exponential in the number of tasks in the worst-case ($t_d = H$).

@@

	\subsection{Existence condition}
	\label{sct:FPDITexist}

		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\begin{equation}
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\end{equation}

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with parameters:
		\begin{itemize}
			\item $U_{tot}$ (system utilization) chosen uniformly between 0.25 and 0.75
			\item $n$ (number of tasks) set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}

>>>>

		The DBF test gives us the following list of inequations on the WCET values of the task set
		which, taken together, are a necessary and sufficient condition of feasibility:
		\begin{equation}
			\sum_{i=1}^{n}  n_i(t_1, t_2) \cdot C_i \leq t_2 - t_1 \; \forall t_1,t_2 \mid 0 \leq t_1 \leq t_2
		\end{equation}
		Note that for given values  of $(t_1, t_2)$, the $n_i(t_1, t_2)$ are
		constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

  To summarize, the description of the C-space is reduced from an infinite number
  of constraints to only those where $t_1 = 0$, $t_2 \leqslant t_d$ and
  values of $t_2$ correspond to job deadlines. Note that the number of
  constraints is still exponential in the number of tasks in the worst-case ($t_d = H$).

@@

	\subsection{Existence condition}
	\label{sct:FPDITexist}
		As in the synchronous case, the problem of existence of the FPDIT
		can be written as a system of modular equations:
		\begin{equation}
			\begin{array}{l}
				\exists ? \; t_d \; s.t. \; \forall \tau_i \in \tau, \exists a_i \in [D_i,
				T_i] \; :\\
				\left\{
					\begin{array}{l}
						t_d > O_i \\
						t_d - O_i \equiv a_i \; (mod \;	T_i)
						\\
					\end{array}
				\right.
			\end{array}
		\end{equation}
        Where $a \equiv b \; (mod \; n)$ means that $a$ and $b$ are congruent modulo $n$.

@@

	We thus checked the existence condition on 10000 systems generated by:
	\begin{itemize}
		\item Generating utilization values with the \texttt{UUniFast} algorithm described in \cite{bini2005measuring}, with:
		\begin{itemize}
			\item The system utilization chosen uniformly between 0.25 and 0.75
			\item The number of tasks set to several values (see Fig.~\ref{fig:noFPDIT})
		\end{itemize}
		\item Choosing the $T_i$ uniformly between 5 and 20 (in order to have a manageable value of $H$), which also gives us the $C_i = \lfloor U_i \, T_i \rfloor$
		\item Choosing the $O_i$ with a normal distribution of mean $T_{min}$ and standard deviation $\frac{T_{max} - T_{min}}{2}$
		\item Choosing the $D_i$ uniformly in the interval $[T_i - CDF(T_i - C_i), T_i]$, where $CDF$ varies between 0 and 1 and is called the \emph{Constrained Deadline Factor}. It allows us to generate systems where the deadlines are closer to the period.
	\end{itemize}
